---
title: "WeatherDataCleaning"
author: "Olga Chyzh"
date: "January 23, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Libraries:
```{r}
library(readr) #Why did you use this?  I kept it, in case you convince me that we need it.
library(tidyverse) #I did not teach you this, but this package, along with magrittr allows for the "piping" approach to R programming, which is clearer to read/follow when collaborating. Primarily, instead of nesting you use pipe-oparators, so the operations are structured from left-to-right rather than from the inside out. It also minimizes the need to create/save intermediate objects that are unecessary for the final output. 
library(magrittr)

```

Set the working directory to "NOAA Data/Daily/"

Write the code for one country-year:
```{r}
opium_ht<-74.3
opium_lt<-42.08

mj_ht<-80.6
mj_lt<-42.8

coca_ht<-77
coca_lt<-64.4

countryfiles<-list.files("./temperature/") #Get a list of filenames in the folder

countryfile<-countryfiles[5] #Why are we starting with 1974? Is that when the GTD start?
cname<- str_extract(countryfile,"\\D+")  %>% str_remove("_") 
year<-str_extract(countryfile,"\\d+")
d<-read.csv(paste("./temperature/",countryfile,sep=""), header=TRUE)%>%
  mutate(TAVG= na_if(TAVG, -9999)) %>% 
  group_by(date=DATE) %>%  
  summarise(TAVG=mean(TAVG,na.rm=TRUE)) %>% 
  ungroup %>%
  mutate(month=substr(date, 5, 6)) %>% 
  group_by(month=month) %>% 
  summarise(ave_mo_t=mean(TAVG ,na.rm=TRUE), opium_t=sum(as.numeric(opium_lt <= TAVG &  TAVG<=opium_ht)),mj_t=sum(as.numeric(mj_lt <= TAVG &      TAVG<=mj_ht)),coca_t=sum(as.numeric(coca_lt <= TAVG &  TAVG<=coca_ht)) ) %>% 
  ungroup %>% 
  mutate(year=year, cname=cname)
d

```

Turn this into a function:

```{r}


get_favtemp<-function(countryfile) {
opium_ht<-74.3
opium_lt<-42.08

mj_ht<-80.6
mj_lt<-42.8

coca_ht<-77
coca_lt<-64.4
  
cname<- str_extract(countryfile,"\\D+")  %>% str_remove("_")
year<-str_extract(countryfile,"\\d+")
cat("file:", countryfile) #This is so that we can quickly identify the source of any errors.
d<-read.csv(paste("./temperature/",countryfile,sep=""), header=TRUE)%>%
  mutate(TAVG= na_if(TAVG, -9999)) %>% 
  group_by(date=DATE) %>%  
  summarise(TAVG=mean(TAVG,na.rm=TRUE)) %>% 
  ungroup %>%
  mutate(month=substr(date, 5, 6)) %>% 
  group_by(month=month) %>% 
  summarise(ave_mo_t=mean(TAVG ,na.rm=TRUE), opium_t=sum(as.numeric(opium_lt <= TAVG &  TAVG<=opium_ht)),mj_t=sum(as.numeric(mj_lt <= TAVG &      TAVG<=mj_ht)),coca_t=sum(as.numeric(coca_lt <= TAVG &  TAVG<=coca_ht)) ) %>% 
  ungroup %>% 
  mutate(year=year, cname=cname)
}

print(get_favtemp(countryfiles[5])) #Test the function on one file before applying it to all

countryfiles<-list.files("./temperature/") #Technically this need not be repeated, but having this line here for now helps to quickly deal with corrupted files
mydata<-lapply(countryfiles[5:length(countryfiles)], get_favtemp)

#Convert to a single dataframe:
mydata<-do.call(rbind, lapply(mydata, data.frame, stringsAsFactors=FALSE))
mydata

```

Notes for Sam.  Can you please check the NOAA website for Russia2002-Russia2009, Russia2011 temperature data (our files did not have the date variable for some reason). I noticed that we also do not have precipitation files for many countries, or that precipitation data are in the same files as the temperature data.


